### 2013-06-30 inst/doc/vingette.Rmd
Updated example XML file and vingette to show new eml_write command option for title.
Fixed typo in variable name that caused bug whereby the entityDescription field was blank, and updated the vignette and example doument to show the description field.
update import dependencies

```{r}
library("devtools")
install_github("XMLSchema", "omegahat")
install_github("reml", "ropensci")
library("reml")
```

@@

```{r}
eml_write(dat, col_metadata, unit_metadata, file="my_eml_data.xml")
```

>>>>

```{r}
install.packages("uuid",,'http://rforge.net/',type='source')
library("devtools")
install_github("XMLSchema", "omegahat")
install_github("reml", "ropensci")
library("reml")
```

@@

```{r}
eml_write(dat, col_metadata, unit_metadata, .title="A test EML file", file="my_eml_data.xml", file_description="Test data, only intended for testing")
```
